\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amsthm, amssymb}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}

\title{WebDB Project Plan}
\author{Phineas Callahan,Yuping Huang}
\begin{document}

 \maketitle

\section{The Data}
The dataset we are planning to use are the historical congressional, gubernatorial and presidential 
election data from CQ Press Voting and Elections Collection (\url{http://library.cqpress.com/elections/index.php}).
We will download the data in csv format. On the “Download Data” page 
(\url{http://library.cqpress.com/elections/download-data.php}),
one has to agree to the condition “these data are to be used for scholarly, educational, or personal use only” 
before proceeding to download. Henceforth academic use of the data should be permitted.

\section{The Audience}
The intended audience of this project (the data and the query interface) are those who are interested in electoral
politics, especially its time evolution. Possible examples include researchers who want to understand historical voting trends in different
regions, students who are studying the change of voters' behaviors over time, political campaign managers who seek
to optimize their campaign strategy, and voters who are interested in the peformances of different parties and politicians
in the past.

\section{Functional\& Non-functional Requirements}
The WebDB project is conceived to have the following functional requirements:
\begin{enumerate}
 \item The system must store all the available congressional, gubernatorial and presidential data by county and congressional district from CQPress.
 \item The system must allow the users to select data based on locations and/or years.
 \item The system must provide appropriate visualization for the set of data selected by the user.
 \item The system must provide appropriate analytics for the set of data selected by the user.
 \item The system must give the users the option to retrive selected data (might be hard in terms of generating csv and the link to download)
\end{enumerate}

Besides, to support its functional requirements, we have specified the following non-functional requirements:
\begin{enumerate}
 \item viz accesibility--color-blindness
 \item response time?
 \item penguins
\end{enumerate}

\section{Key Features}
The WebDB project should have the following features. The list is ordered in decsending priorities. Time and resources
permitting, we aim to implement all of them.
\begin{enumerate}
 \item a map, and more maps
 \item a traditional query interface (dropdown lists)
 \item time series viz
 \item breakdown pie chart
 \item download button
 \item a lot of buttons
 \item animations for transitions
 \item menu element(maybe)
\end{enumerate}

\section{UI Mockup}
\end{document}
